\documentclass[12pt]{report} 

% language may be romanian or english (default is english)
% type may be bachelor or master (default is bachelor)
\usepackage[language=romanian, type=bachelor]{style}

%\geometry{a4paper,top=2.5cm,left=3cm,right=2.5cm,bottom=2.5cm}
%in style
%controlling the appearance of your headers and footers
\usepackage{fancyhdr}    
\pagestyle{fancy}
\lhead{}
\chead{}
\renewcommand{\headrulewidth}{0.2pt}
\renewcommand{\footrulewidth}{0.2pt}

\usepackage{listings}
\usepackage{xcolor}
\renewcommand{\lstlistingname}{Secvența de cod}
\lstdefinestyle{pythonstyle}{
    language=Python,
    basicstyle=\ttfamily\footnotesize,
    keywordstyle=\color{blue}\bfseries,
    commentstyle=\color{green!60!black}\itshape,
    stringstyle=\color{red},
    numberstyle=\tiny\color{gray},
    numbers=left,
    numbersep=8pt,
    stepnumber=1,
    backgroundcolor=\color{gray!5},
    frame=single,
    frameround=tttt,
    rulecolor=\color{gray!30},
    breaklines=true,
    breakatwhitespace=false,
    tabsize=4,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    captionpos=b,
    aboveskip=\medskipamount,
    belowskip=\medskipamount
}
\lstset{style=pythonstyle}

\begin{document}

\specialization{INFORMATICĂ ÎN LIMBA ROMÂNĂ}	
\title{Conectarea persoanelor bazată pe interese comune folosind sisteme de recomandare}					   
\author{Bucilă Mihai-Cristian}											
\supervisor{Asist. Drd. Coste Claudia-Ioana \\ Prof. univ. Dr. Andreica Anca-Mirela}				
				
\maketitle


\newpage
\thispagestyle{empty}
\mbox{}
\newpage
\pagenumbering{roman} 

\cleardoublepage
ABSTRACT
\vspace{0.5cm}	
\hrule
\vspace{0.5cm}	
%\cleardoublepage

\par
The abundance of information on the internet has driven the rapid evolution of recommender systems.
Their ability to provide personalized suggestions has led to widespread adoption in high-demand areas like e-commerce and social networking platforms, enhancing both user experience and retention.
\par
This thesis presents the core techniques underlying recommendation systems --- content-based filtering and collaborative filtering --- and explores the challenges that can arise when implementing these methods, such as the cold start problem, synonymy and privacy concerns.
The main objective of this work is to demonstrate the utility of a recommender system in the context of an application that matches users based on their shared hobbies.
The application analyzes user-provided hobby data and uses a simplified matching algorithm to identify potential matches within a shared interest space.
\par
This work is motivated by the idea that recommender systems can have an impact beyond commercial platforms and enhance social connectivity and community building.
By combining the theoretical knowledge with a concrete implementation, the project shows how recommendation techniques can be adapted to support social engagement and personal development.
The application serves not only as a case study, but also as a proof of concept for using technology to bring people together in a more intentional way.
\par
This paper is organized into five chapters that address both theoretical background and practical solution.
The first chapter introduces the topic, exposing the main objectives and the motivation behind the research.
The second chapter reviews several existing recommendatation system solutions and studies.
Chapter 3 provides the theoretical concepts which are essential to understand the proposed approach.
Chapter 4 presents the developed software solution.
Finally, the last chapter summarizes the work and mentions potential directions for future work.


\tableofcontents


\newpage
\pagenumbering{arabic}

\input{chapters/chapter1_introduction}
%\addcontentsline{toc}{chapter}{Introducere}
%\addcontentsline{toc}{chapter}{Introduction}

\input{chapters/chapter2}
\input{chapters/chapter3}
\input{chapters/chapter4}

\input{chapters/chapter5_conclusions}
%\addcontentsline{toc}{chapter}{Concluzii}
%\addcontentsline{toc}{chapter}{Conclusions}

\bibliography{references}

\end{document}
